Modeling Intervention Strategies for United States TB Control

### 2013-08-24 in_progress/presentations/paper/draft.tex
tightened up interventionTable.R and incorporated some results into draft

\subsection{Intervention Analysis}
The primary interventions analyzed by the extended Hill were those that analyzed
curing various percentages of entering LTBI cases. Four indicative percentages
chosen were $20\%$, $35\%$, $50\%$, and $65\%$. Note that the hill model does
not distinguish documented immigration from undocumented immigration, and as
such estimates of entering LTBI cure rates higher than $65\%$ become much more
difficult to acheive. It was seen that in this model as well as in the basic
Hill, no analyzed intervention predicted elimination by 2100. In order to obtain
elimiation by 2100, at least 95\% of entering LTBI cases had to be cured, which
is practically impossible. However, it was seen that curing entering cases of
LTBI resulted in a net US HCS cost per case averted of \$X at 2025, \$Y at 2050,
and \$Z at 2100. Further, it was also found that the relationship between total
incidence at 2100 and percentage of incoming LTBI cases cured was linear, and
from this estimates were made of the yearly average US HCS savings garnered by
curing one case of entering LTBI over the time scale 2000 to 2025, 2000 to 2050,
and 2000 to 2100. This value peaked at \$X at 2100. This illustrates that it
would be cost saving to cure cases of LTBI at the cost of X 2000 dollars over
the time period 2000-2100. These intervention strategies also resulted in A, B,
and C fewer cases of TB seen in the US, and D, E, and F fewer TB
deaths, respectively.

>>>>

\subsection{Intervention Analysis}
The primary interventions analyzed by the extended Hill were those that analyzed
curing various percentages of entering LTBI cases. Four indicative percentages
chosen were $20\%$, $35\%$, $50\%$, and $65\%$. Note that the hill model does
not distinguish documented immigration from undocumented immigration, and as
such estimates of entering LTBI cure rates higher than $65\%$ become much more
difficult to achieve. It was seen that in this model as well as in the basic
Hill, no analyzed intervention predicted elimination by 2100. In order to obtain
elimination by 2100, at least 95\% of entering LTBI cases had to be cured, which
is practically impossible. However, it was seen that curing entering cases of
LTBI resulted in a net US HCS cost per case averted of \$67,722.96 at 2025, \$28,759.00 at 2050,
and \$17,967.39 at 2100 (assuming 20\% reduction with one cure costing \$XXXX; see Table
\ref{tab:cpcaRes} for other percentages). Further, it was also found that the relationship
between total incidence at 2100 and percentage of incoming LTBI cases cured was linear, and
from this estimates were made of the yearly average US HCS savings garnered by
curing one case of entering LTBI over the time scale 2000 to 2025, 2000 to 2050,
and 2000 to 2100. This value peaked at \$X at 2100. This illustrates that it
would be cost saving to cure cases of LTBI at the cost of X 2000 dollars over
the time period 2000-2100. These intervention strategies also resulted in A, B,
and C fewer cases of TB seen in the US, and D, E, and F fewer TB
deaths, respectively.

% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Sat Aug 24 18:08:52 2013
\begin{table}
\centering
\begin{tabular}{|r|cccc|}
  \hline
 & red20 & red35 & red50 & red65 \\ 
  \hline
2000 & ND & ND & ND & ND \\ 
  2025 & 67722.96 & 67527.15 & 67332.53 & 67138.90 \\ 
  2050 & 28759.00 & 28581.09 & 28404.13 & 28227.50 \\ 
  2075 & 20876.80 & 20709.13 & 20541.77 & 20374.49 \\ 
  2100 & 17967.39 & 17804.94 & 17642.64 & 17480.33 \\ 
   \hline
\end{tabular}
\caption{Cost Per Case Averted by Reducing Incoming LTBI by 20\%, 35\%, 50\%, and 65\% (in dollar per case)} 
\label{tab:cpcaRes}
\end{table}
